---
title: "Stock Data Analysis"
author: "Lei Fang"
output: pdf_document
header-includes:
  - \usepackage{color}
---

```{r include = FALSE}
library(readxl)
library(pastecs)
library(xts)
```

The goal is to find a strategy that uses the fact that this ETF is constantly going down, in order to make a daily compounding profit.

# \color{blue}What we have
* [UVXY](http://www.nasdaq.com/symbol/uvxy)
    + Daily Open/Close Prices
    + Daily High/Low Prices
    + Daily Volume
    + Split-Adjusted Equivalent Open/Close Prices
* [VIX](https://en.wikipedia.org/wiki/VIX)
    + Daily Open/Close Prices


# \color{blue} Descriptive Analysis

```{r include = FALSE}
# read Excel data file
stock_data = read_excel("/Users/lei.fang/Desktop/R-Markdown/Stock Data Analysis/stock_data_for_lei.xlsx", sheet = 1, col_names = TRUE)
Date           = stock_data$Date
UVXY_Open      = stock_data$Open
UVXY_Close     = stock_data$Close
UVXY_High      = stock_data$High
UVXY_Low       = stock_data$Low
UVXY_Volume    = stock_data$Volume
UVXY_Adj_Open  = stock_data$`Adj_Open`
UVXY_Adj_Close = stock_data$`Adj_Close`
VIX_Open       = stock_data$`Vix_Open`
VIX_Close      = stock_data$`Vix_Close`
attach(stock_data)
UVXY      = cbind(Date, Open, Close, Adj_Open, Adj_Close, High, Low, Volume)
UVXY_desc = cbind(Open, Close, Adj_Open, Adj_Close, High, Low, Volume)
VIX       = cbind(Date, Vix_Open, Vix_Close)
VIX_desc  = cbind(Vix_Open, Vix_Close)
```

```{r warning = FALSE}
library(knitr)
options(scipen = 100)
options(digits = 2)
kable(stat.desc(UVXY_desc, desc = F), caption = "UVXY Descriptive Table")
kable(stat.desc(VIX_desc, desc = F), caption = "VIX Descriptiv Table")
```


# \color{blue} Task 1
For example, consider you short sell UVXY every morning and buy to cover at the end of every day. On average, how profitable would this strategy be?

- Time Series Plot of **Log Split-Adjusted Equivalent Open/Close Prices**
```{r}
plot(Date, log(UVXY_Adj_Open), ylab = "Price", col = "red", type = "l", lwd = 2)
lines(Date, log(UVXY_Adj_Close), col = "blue")
legend('topright', legend = c('Open Price', 'Close Price'), col = c("red","blue"), lty=1)
```

- Time Series Plot of **Daily Open/Close Prices**
```{r}
plot(Date, UVXY_Open, ylab = "Price", col = "red", type = "l", lwd = 2)
lines(Date, UVXY_Close, col = "blue")
legend('topright', legend = c('Open Price', 'Close Price'), col = c("red","blue"), lty=1)
```

- Suppose we trade 100 shares of UVXY per day and we use original daily UVXY open/close price,
```{r}
daily_profit_ave = mean((UVXY_Open - UVXY_Close)*100)
daily_profit_max = max((UVXY_Open - UVXY_Close)*100)
daily_profit_min = min((UVXY_Open - UVXY_Close)*100)
```
| Daily Profit based on 100 Shares | Average | Max | Min |
|---------------------------------:|--------:|----:|----:|
|                                  |`r daily_profit_ave`|`r daily_profit_max`|`r daily_profit_min`|


# \color{blue} Task 2
What was the return of this strategy every year on a yearly basis, 2011-present?

```{r include= FALSE}
# seperate data by years
data = xts(stock_data[,-1], stock_data[,1])
data2011 = data["2011"]
data2012 = data["2012"]
data2013 = data["2013"]
data2014 = data["2014"]
data2015 = data["2015"]
data2016 = data["2016"]
data2017 = data["2017"]
```

- \color{blue} **2011**

```{r}
plot(data2011$Open-data2011$Close, ylab = "Profit", 
     main = "Time Series of Daily Profit per Share")
```

| Daily Profit based on 100 Shares | Average | Max | Min |
|---------------------------------:|--------:|----:|----:|
|                                  |`r mean(data2011$Open-data2011$Close)*100`|`r max(data2011$Open-data2011$Close)*100`|`r min(data2011$Open-data2011$Close)*100`|

- \color{blue} **2012**

```{r echo = FALSE}
plot(data2012$Open-data2012$Close, ylab = "Profit", 
     main = "Time Series of Daily Profit per Share")
```

| Daily Profit based on 100 Shares | Average | Max | Min |
|---------------------------------:|--------:|----:|----:|
|                                  |`r mean(data2012$Open-data2012$Close)*100`|`r max(data2012$Open-data2012$Close)*100`|`r min(data2012$Open-data2012$Close)*100`|

- \color{blue} **2013**

```{r echo = FALSE}
plot(data2013$Open-data2013$Close, ylab = "Profit", 
     main = "Time Series of Daily Profit per Share")
```

| Daily Profit based on 100 Shares | Average | Max | Min |
|---------------------------------:|--------:|----:|----:|
|                                  |`r mean(data2013$Open-data2013$Close)*100`|`r max(data2013$Open-data2013$Close)*100`|`r min(data2013$Open-data2013$Close)*100`|

- \color{blue} **2014**

```{r echo = FALSE}
plot(data2014$Open-data2014$Close, ylab = "Profit", 
     main = "Time Series of Daily Profit per Share")
```

| Daily Profit based on 100 Shares | Average | Max | Min |
|---------------------------------:|--------:|----:|----:|
|                                  |`r mean(data2014$Open-data2014$Close)*100`|`r max(data2014$Open-data2014$Close)*100`|`r min(data2014$Open-data2014$Close)*100`|

- \color{blue} **2015**

```{r echo = FALSE}
plot(data2015$Open-data2015$Close, ylab = "Profit", 
     main = "Time Series of Daily Profit per Share")
```

| Daily Profit based on 100 Shares | Average | Max | Min |
|---------------------------------:|--------:|----:|----:|
|                                  |`r mean(data2015$Open-data2015$Close)*100`|`r max(data2015$Open-data2015$Close)*100`|`r min(data2015$Open-data2015$Close)*100`|

- \color{blue} **2016**

```{r echo = FALSE}
plot(data2016$Open-data2016$Close, ylab = "Profit", 
     main = "Time Series of Daily Profit per Share")
```

| Daily Profit based on 100 Shares | Average | Max | Min |
|---------------------------------:|--------:|----:|----:|
|                                  |`r mean(data2016$Open-data2016$Close)*100`|`r max(data2016$Open-data2016$Close)*100`|`r min(data2016$Open-data2016$Close)*100`|

- \color{blue} **2017**

```{r echo = FALSE}
plot(data2017$Open-data2017$Close, ylab = "Profit", 
     main = "Time Series of Daily Profit per Share")
```

| Daily Profit based on 100 Shares | Average | Max | Min |
|---------------------------------:|--------:|----:|----:|
|                                  |`r mean(data2017$Open-data2017$Close)*100`|`r max(data2017$Open-data2017$Close)*100`|`r min(data2017$Open-data2017$Close)*100`|


# \color{blue} Further Thinking
For example, considering the VIX (volatility index) as part of the calculation or excluding certain days of the week.

- Time Series Plot of **Daily UVXY Open Prices**, **VIX Open Prices** and **Daily Profit per Share**
```{r}
plot(data$Open-data$Close, ylim = c(-12, 100), ylab = "Price / Profit", 
     main = "UVXY/VIX Open Price and Daily Profit per Share")
lines(Date, UVXY_Open, col = "red")
lines(Date, VIX_Open, col = "blue")
legend('topright', legend = c('Profit', 'UVXY', 'VIX'), 
       col = c("black", "red","blue"), lty=1)
```

- Time Series Plot of **VIX Open Prices** and **Daily Profit per Share**
```{r}
plot(data$Open-data$Close, ylim = c(-12, 50), ylab = "Price / Profit", 
     main = "VIX Open Price and Daily Profit per Share")
lines(Date, VIX_Open, col = "blue")
legend('topright', legend = c('Profit', 'VIX'), 
       col = c("black", "blue"), lty=1)
```
